Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-08 ms/manuscript.Rmd
Fix link to docker image

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/japan_ferns_spatial_phy. 
A Docker image to run the code is available at https://hub.docker.com/repository/docker/joelnitta/japan_ferns_spatial_phy.
Data files needed to run the analysis and selected results files are available from Dryad at http://doi.org/ADD_DOI_HERE_WHEN_ASSIGNED.

>>>>

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/japan_ferns_spatial_phy. 
A Docker image to run the code is available at https://hub.docker.com/r/joelnitta/japan_ferns_spatial_phy.
Data files needed to run the analysis and selected results files are available from Dryad at http://doi.org/FIXME:ADD_DOI_HERE_WHEN_ASSIGNED.
